A Comparison of Graph Processing Systems

### 2020-09-23 documentation/paper/main.tex
kleine Korrekturen

\begin{IEEEkeywords}
graphs, distributed computing, Galois, Ligra, Polymer, Giraph, Gluon, Gemini
\end{IEEEkeywords}

@@

>>>>

\begin{IEEEkeywords}
graphs, distributed computing, Galois, Ligra, Polymer, Giraph, Gluon, Gemini, SSSP, BFS, PR, benchmark
\end{IEEEkeywords}

@@

\bibitem{hybridBFS}
S.~{Beamer}, K.~{Asanovic}, and D.~{Patterson}, ``Direction-optimizing
  breadth-first search,'' in \emph{SC '12: Proceedings of the International
  Conference on High Performance Computing, Networking, Storage and Analysis},
  2012, pp. 1--10.
